The Globular Cluster System of the Auriga Simulations

### 2019-03-27 AurigaGCS.tex
Images for Sec. 4.3 v0.1

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_iold_mean}.png}
    \caption{
        Mass-weighted [Fe/H]-$R_{\text{GC}}$ distribution of all Auriga haloes
        (level 3, 4 and 5). Here we consider the old ($>$~10~Gyr) stars in all
        simulations and color-code the \textbf{mean value} (of 40 Auriga haloes)
        \label{fig:Au-FeHRgc}
    }
\end{figure}

\subsection{Total mass in metallicity-radial space}
We investigate whether the Auriga simulations still produce sufficient mass in 
old star particles to be consistent with the MW (M31) GCS when two-dimensionally 
binned in both [Fe/H] and $R_\text{GC}$. We sum the total simulated mass in 
each bin and then divide it by the total mass in the MW (M31) GCS. We show this
mass excess in Figure~\ref{}, respectively Figure~\ref{}
\label{sec:results_FeHRgc}
\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_iold_36bins_mean-trim}.png}
    \caption{
        Ratio
        \label{fig:Au-FeHRgc-ratio}
    }
\end{figure}

>>>>

\subsection{Total mass in metallicity-radial space}
\label{sec:results_FeHRgc}

We investigate whether the Auriga simulations still produce sufficient mass in 
old star particles to be consistent with the MW (M31) GCS when two-dimensionally 
binned in both [Fe/H] and $R_\text{GC}$. We sum the total simulated mass in 
each bin and then divide it by the total mass in the MW (M31) GCS. We show this
mass excess in Figure~\ref{}, respectively Figure~\ref{}
\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_iold_36bins_mean}.png}
    \caption{
        Mass-weighted [Fe/H]-$R_{\text{GC}}$ distribution of all Auriga haloes
        (level 3, 4 and 5). Here we consider the old ($>$~10~Gyr) stars in all
        simulations and color-code the \textbf{mean value} (of 40 Auriga haloes)
        \label{fig:Au-FeHRgc}
    }
\end{figure}

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_MW_iold_36bins_mean}.png}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_M31_iold_36bins_mean}.png}
    \caption{
        Caption
        \label{fig:Au-FeHRgc-ratio}
    }
\end{figure}
